---
title: "Peer Assessment 1"
author: "Aviv Zach"
date: "Tuesday, April 14, 2015"
output: html_document
---

### Loading and preprocessing the data
```{r}
unzip("activity.zip")
rowdata<-read.csv("activity.csv")
```


### Mean total number of steps taken per day
Total number of steps taken per day:
```{r}
tot_steps_d<-sapply(split(rowdata$steps,rowdata$date),sum,na.rm=TRUE)
tot_steps_d
```
Histogram of the total number of steps taken each day:
```{r}
hist(tot_steps_d,xlab="Total Steps Per Day",main = "Histogram of Total Steps Per Day" )
```

Mean and Meadian are: 
```{r}
mean(tot_steps_d)
median(tot_steps_d)
```


###Average daily activity pattern
Time series plot of the 5-minute interval and the average number of steps taken:
```{r}
avg_steps_int<-sapply(split(rowdata$steps,rowdata$interval),mean,na.rm=TRUE)
plot(names(avg_steps_int),avg_steps_int,type="l",ylab="Average Steps", xlab="Interval",main="Average Steps in each Interval")
```

The 5-minute interval that contains the maximum number of steps,on average is: 
```{r}
names(which(avg_steps_int==max(avg_steps_int)))
```


### Imputing missing values
Total number of missing values in the dataset:
```{r}
sum(is.na(rowdata))
```
I will use the mean for the 5-minute interval.
New dataset with no missing values:
```{r}
goodata<-rowdata
goodata$steps[is.na(goodata[,1])]<-avg_steps_int[match(goodata[is.na(goodata[,1]),3],names(avg_steps_int))]
```
Histogram,Mean and Median of the total number of steps taken each day:
```{r}
tot_steps_d_good<-sapply(split(goodata$steps,goodata$date),sum)
hist(tot_steps_d_good,xlab="Total Steps Per Day",main = "Histogram of Total Steps Per Day,No miising Values" )
mean(tot_steps_d_good)
median(tot_steps_d_good)
```
yes, these resaults are diffrent. the median and mean are the same - the histogram is more centralized .


### differences in activity patterns between weekdays and weekends
New factor variable in the dataset with two levels “weekday” and “weekend”:
```{r}
days<-weekdays(as.Date(goodata$date))
goodata$days[days %in% unique(days)[1:4]]<-"weekday"
goodata$days[days %in% unique(days)[5:7]]<-"weekend"
goodata$days<-factor(c("weekday","weekend"))
```
Panel plot containing a time series plot of the 5-minute interval and the average number of steps taken,on weekdays and weekends:
```{r}
library(lattice)
wkd<-goodata[goodata$day=="weekday",]
wnd<-goodata[goodata$day=="weekend",]
wkdsteps<-sapply(split(wkd$steps,wkd$interval),mean)
wndsteps<-sapply(split(wnd$steps,wnd$interval),mean)
df1<-data.frame(interval=names(wkdsteps),mean=wkdsteps)
df1$day<-"weekday"
df1$interval<-as.numeric(as.character(df1$interval))
df2<-data.frame(interval=names(wndsteps),mean=wndsteps)
df2$day<-"weekend"
df2$interval<-as.numeric(as.character(df2$interval))
finaldata<-rbind(df1,df2)
xyplot(mean ~ interval|day,data=finaldata,layout=c(1,2),type = "l", xlab= "Interval",ylab="Average Number of Steps")
```